---
title: "R Notebook Data Sanitization"
output: html_notebook
---

This Notebook illustrates how the customer records are debased to reflect nuances of real-world data.

####Setup the Environment

Set up the root folder, load libraries and helper functions.
```{r, message=FALSE}
knitr::opts_knit$set(root.dir = "F:/GitHub/deduplication/src")
source("config/libraries.R")
source("lib/helpers.R")

```


####Read the original dataset
Read the 100% clean customer records from the previous notebook. This represents an ideal scenario.  This dataset has to be sanitized to reflect quality issues in the real-world scenario.

```{r}
modified.data <- read.csv(file="data/base.ds.200k.csv", stringsAsFactors = FALSE)

```

####Create clones to reflect scenarios in real-world data

Create a data frame to store duplicated records
```{r}
dupli.ds <- data.frame(matrix(0, ncol = ncol(modified.data), nrow = 0))
colnames(dupli.ds) <- colnames(modified.data)
```

Reorganizing the datatype of certain columns

```{r}
dupli.ds$someid <- as.character(dupli.ds$someid)
dupli.ds$mnumber <- as.character(dupli.ds$mnumber)
dupli.ds$hnumber <- as.character(dupli.ds$hnumber)
dupli.ds$birth.date <- as.character(dupli.ds$birth.date)
dupli.ds$postcode <- as.character(dupli.ds$postcode)
```


#####Create a dataframe to store non-duplicated records
```{r}
non.dupli.ds <- dupli.ds

```


#####Set a percentage value for the number of customer clones to be created.
Within this, 4% of the original dataset will be cloned.  These are duplicate records that would need to be identified correctly by the deduplication engine.

The cloned customer records will have the same address.
```{r}
# p <- 4 #Experiment1
# p <- 8 #Experiment2
p <- 12
temp.ds <- clonePerson(modified.data, p)
dupli.ds <- rbind(dupli.ds, temp.ds$clones)

dupli.ds <- dupli.ds[!duplicated(dupli.ds$recoid),]
```


#####Duplicate Records for identical Twins living in the same address,
```{r}
# pt <- 0.25
# pt <- 0.5 #Experiment2
pt <- 0.75
#also pass the list of record ids that has been used.
temp.ds <- createTwins(temp.ds$ds.99, pt)
non.dupli.ds <- rbind(non.dupli.ds, temp.ds$twins) # Non-duplicates means individual people
non.dupli.ds <- non.dupli.ds[!duplicated(non.dupli.ds$recoid),]

```



#####Duplicate Records for neighbors living in the same apartment,

```{r}
# pn <- 0.04 #experiment 1
# pn <- 0.08 #Experiment2
pn <- 0.12
## also pass the list of record ids that has been used.
temp.ds <- createNeighbors(temp.ds$ds.99, pn)
non.dupli.ds <- rbind(non.dupli.ds, temp.ds$neighbors) # Non-duplicates means individual people
non.dupli.ds <- non.dupli.ds[!duplicated(non.dupli.ds$recoid),]

```

#####Duplicate Records for Married couples living in the same address
The assumption is that 15% of the customer base will be married couples living in the same address.   This can be changed by changing the value for "pc".
```{r}
# % of couples in the loan availing population = 50%
# % of couples living in the same address = 80%
# Combined percentage of the above = 40%
#pc <- 15 #experiment 1
# pc <- 20  #experiment 2
pc <- 25
temp.ds <- createCouples(temp.ds$ds.99, pc)
non.dupli.ds <- rbind(non.dupli.ds, temp.ds$couples)

```

#####The duplicate records and bound to the original dataset
All the above records are bound to the original dataset.
```{r}
modified.data <- rbind(modified.data, dupli.ds)
modified.data <- rbind(modified.data,non.dupli.ds)

record.count <- nrow(modified.data)
```

#####The new record count
The new record count is 267,315. 

####Introduce other kinds of errors that could be prevalent in real-world data.


#####Create Typographical errors name to simulate spelling mistakes
```{r, message=FALSE, warning=FALSE, include=FALSE}
# pe <- 0.04 #experiment 1
# pe <- 0.08 #Experiment2
pe <- 0.12
modified.data <- makeTypos(modified.data, "John", "Jon", pe)
modified.data <- makeTypos(modified.data, "Thompson", "Thomson", pe)
modified.data <- makeTypos(modified.data, "tt", "t", pe)
modified.data <- makeTypos(modified.data, "ss", "s", pe)
```


simulate missing email id - write into the base dataset
```{r message=FALSE, warning=FALSE, include=FALSE}
# p <- 4 #experiment 1
# p <- 6 #Experiment2
p <- 8
modified.data$email[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

simulate missing home phone numbers
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$hnumber[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

Missing Mobile phone numbers
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$mnumber[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

Simulate missing postcodes
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$postcode[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

Simulate Missing Address 1 from Address
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$addr1[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

simulate Missing Address 2 from Address
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$addr2[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

Simulate Missing County Name from Address
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$county[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

Simulate Missing City Name from Address
```{r message=FALSE, warning=FALSE, include=FALSE}
modified.data$cityname[sample(nrow(modified.data), nrow(modified.data) * p / 100)] <- ''

```

####Write the Sanitized file
Write the sanitized file into a .csv format to be reused later.  

```{r message=FALSE, warning=FALSE, include=FALSE}
write.csv(modified.data,file="data/exp3.modified.data.csv", row.names = FALSE ,quote=c(1:15) )

```

