---
title: "R Notebook"
output: html_notebook
---

This notebook does the pre-processing to create the customer records.

####Setup the environment

1. Setup the working directory
2. Load the required libraries from config/libraries.R
3. Load the help functions from lib/helpers.R

```{r, message=FALSE, warning=FALSE, include=FALSE}
setwd("F:/GitHub/deduplication/src")
wd <- getwd()
setwd("..")
parent <- getwd()
setwd(wd)
source("config/libraries.R")
source("lib/helpers.R")
```



####Read the customer records from the CSV file

```{r}
cust.rcds = read.csv(file="data/customers-200k.csv")
colnames(cust.rcds)
```

####Column filters for the dataset

```{r}
col.filter <- c("userid","someid","firstname","lastname",
                "gender","birthdate","email","mobilenumber",
                "homenumber","address1","address2","cityname","postcode",
                "county","nis")
```


####Creating a dataset with just the required columns
```{r}
base.ds.200k <- cust.rcds[col.filter]
```


####Renaming columns in the dataset
```{r}
col.names <-  c("recoid","someid","firstname","lastname",
                  "gender","birthdate","email","mnumber",
                  "hnumber","addr1","addr2","cityname","postcode",
                  "county","nis")
colnames(base.ds.200k) <- col.names
```



####Format the date of birth field
```{r}
base.ds.200k$birthdate <- as.POSIXct(base.ds.200k$birthdate, format='%Y-%m-%d')
base.ds.200k$birthdate <- as.Date(base.ds.200k$birthdate, format='%Y-%m-%d')
```


####Column Descriptions for the report

```{r}
desc.base.ds.200k <- as.data.frame(t(base.ds.200k[1,]))
desc.base.ds.200k$variables <- rownames(desc.base.ds.200k)
rownames(desc.base.ds.200k) <- NULL
colnames(desc.base.ds.200k)<- c("Description","Variable")
desc.base.ds.200k$Description <- c("Unique ID in the dataset","Some Org ID","First Name","Last Name","Gender",
                              "Date of Birth","e-mail ID","Mobile Number",
                              "Home Number","Home Nummber","Street Address",
                              "Name of the City","Post Code","Country","National Insurance Number")

desc.base.ds.200k$No. <- c(1:nrow(desc.base.ds.200k))
desc.base.ds.200k <-desc.base.ds.200k[,c(3,2,1)]
write.csv(desc.base.ds.200k, file="desc.base.ds.200k.csv")
#------------------------------------------------------------------------------------------------
```

####Splitting the Date of Birth field into three individual columns

```{r}
base.ds.200k$b.year <- format(base.ds.200k$birthdate, format='%y')
base.ds.200k$b.month <- format(base.ds.200k$birthdate, format='%m')
base.ds.200k$b.day <- format(base.ds.200k$birthdate, format='%d')
```


####Convert cont.id and someid to characters as required, for string comparison

```{r}
base.ds.200k$someid <- as.character(base.ds.200k$someid)
base.ds.200k$mnumber <- as.character(base.ds.200k$mnumber)
base.ds.200k$hnumber <- as.character(base.ds.200k$hnumber)
base.ds.200k$birthdate <- as.character(base.ds.200k$birthdate)
base.ds.200k$email <- as.character(base.ds.200k$email)
base.ds.200k$addr1 <- as.character(base.ds.200k$addr1)
base.ds.200k$addr2 <- as.character(base.ds.200k$addr2)
base.ds.200k$county <- as.character(base.ds.200k$county)
base.ds.200k$postcode <- as.character(base.ds.200k$postcode)
base.ds.200k$nis <- as.character(base.ds.200k$nis)
```


####Write the pre-processed dataframe into a csv file

```{r}
write.csv(base.ds.200k, file="data/base.ds.200k.csv")

remove(cust.rcds)

```

####Pre processing complete

The preprocess is complete and 200,000 customer records are available in the file base.ds.200k.csv.



